Poseidon Adventure

### 2019-05-22 Atlantisom2SSworkflowtest.Rmd

# initial conditions file has different structure, so drop [,1]
at_init <- RNetCDF::open.nc(con = file.path(d.name, initial.conditions.file))
on.exit(RNetCDF::close.nc(at_init))

@@

@@

#save for later use, ar (better) resave truth file
#saveRDS(catch, file.path(d.name, paste0(scenario.name, "catchnums_corrected.rds")))
  save(truth,
      file = file.path(dir, paste0("output", scenario, "run_truth.RData")))
```

>>>>

# initial conditions file has different structure, so drop [,1]
at_init <- RNetCDF::open.nc(con = file.path(d.name, initial.conditions.file))

@@

  RNetCDF::close.nc(at_init)

@@

#save for later use, ar (better) resave truth file
#saveRDS(catch, file.path(d.name, paste0(scenario.name, "catchnums_corrected.rds")))
  save(truth,
      file = file.path(d.name, paste0("output", scenario.name, "run_truth.RData")))
```

### 2019-05-22 docs/index.Rmd

<a href="https://sgaichas.github.io/poseidon-dev/Atlantisom2SSworkflowtest.html" target="_blank">Try for true datasets new CC model with climate - May 21, 2019</a>

@@

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/Atlantisom2SSworkflowtest.html" target="_blank">Try for true datasets new CC model with climate - May 21, 2019, updated May 22, 2019 with catch correction</a>

@@

<a href="https://sgaichas.github.io/poseidon-dev/TestCatchNOBA.html" target="_blank">Suggests a workaround needed for catch in weight - May 21, 2019</a>
